---
title: "Homework 2 - R Exercises"
output: html_notebook
---

## Exercise 3. Mean of sulfate values in pollution monitoring data
```{r}
# Scan and get name of all CSV files
fnames = list.files(path = "specdata/.", pattern = "*.csv")
# Sum of sulfate values in all CSV files
sum_sulfate = 0
# Number of monitored days
observered_days = 0
# Calculating sum of sulfate values and number of observered days
for (i in 1:length(fnames)) {
  # Read i-th CSV file into R
  assign(fnames[i], read.csv(paste("specdata/", fnames[i], sep = "")))
  # Get sulfate values in i-th CSV file
  sulfate_values = get(fnames[i])$sulfate
  # Summing available values of sulfate
  sum_sulfate = sum_sulfate + sum(sulfate_values, na.rm = T)
  # Calculate number of observered days
  for (j in 1:length(sulfate_values)) {
    if (!is.na(sulfate_values[j]))
      observered_days = observered_days + 1
  }
}

# Mean of sulfate across all locations for all days
sprintf("Mean value of sulfate is %f", sum_sulfate/observered_days)
```

## Exercise 4. Groceries data set with arules package

#### 4.1. Obtain some information about data set
```{r}
# Load arules package
library("arules")
# Load groceries data set
data("Groceries")
# (i) Most frequent item (We can also get this from summary(Groceries))
GrocTidLists <- as(Groceries, "tidLists")
mostFrequentItem = GrocTidLists[which.max(size(GrocTidLists))]
print(paste("Most frequent item is", itemLabels(mostFrequentItem)))
# (ii) Length of longest transactions
length_longest = max(size(Groceries))
sprintf("Length of longest transactions is %d", length_longest)
# (iii) First five transactions (transactionInfo() does not give any information)
inspect(Groceries[1:5])
```
</br>

#### 4.2. Mine all association rules with min_sup = 0.001 and min_conf = 0.8
```{r}
rules = apriori(Groceries, parameter = list(support = 0.001, confidence = 0.8))
```
</br>

#### 4.3. Draw scatter plot for all association rules
```{r}
# Load arulesViz package
library("arulesViz")
# Plot rules
plot(rules)
```
</br>

#### 4.4. Print top-3 association rules according to the lift
```{r}
# Get the 3 rules having highest lift values
top_rules_by_lift = head(sort(rules, by = "lift"), n = 3)
# Print the rules
labels(top_rules_by_lift)
```
</br>

#### 4.5. Draw top-3 association rules as a graph such that a node becomes an item
```{r}
plot(top_rules_by_lift, method="graph", shading = "lift")
```
