---
title: "KSE525 HW4 - R Exercise"
output: html_notebook
---

## Exercise 5. k-means algorithm

```{r}
# Load data
data(wine, package = "rattle.data")
```

```{r}
# center and scale wine dataset without labels
df <- scale(wine[-1])
```

```{r}
# wssplot function
wssplot <- function(data, nc=15, seed=1234){
    wss <- (nrow(data)-1)*sum(apply(data,2,var))
    for (i in 2:nc) {
        set.seed(seed)
        wss[i] <- sum(kmeans(data, centers=i)$withinss)
    }
    plot(1:nc, wss, type="b", xlab="Number of Clusters",
         ylab="Within groups sum of squares")
}
```
</br>

### 1). wssplot function
```{r}
wssplot(df)
```

#### The wssplot function draws a graph with **x axis** as number of clusters, and **y axis** as the within-group sum of squares corresponding to the number of clusters.
#### Looking at the graph above, starting from cluster number of 3, the value of within-group sum of squares starts not to decrease rapidly. Therefore, the good number of clusters (k) is 3.
</br>

### 2). Perform **k-means** clustering with the value of _k_ obtained in 1).
```{r}
# Set seed value
set.seed(1234)
kmeans_obj = kmeans(df, 3, nstart=25)
# Print number of points assigned to each cluster
print(kmeans_obj$size)
```
</br>

### 3). Calculate variable means for each cluster in the original metric
```{r}
aggregate(wine[-1], list(kmeans_obj$cluster), mean)
```
</br>

### 4). Print out the confusion matrix
```{r}
table(kmeans_obj$cluster, wine$Type)
```
#### Looking at the confusion matrix above, we see that there are 3 records of Type 3 which are incorrectly assigned to cluster of Type 2.

