---
title: "Homework 3 - R Exercises"
output: html_notebook
---

## Exercise 4. Decision Tree

#### 4.1 Build and plot decision tree for GlaucomaM data set
```{r}
library("party")
data("GlaucomaM", package = "TH.data") # Load data
# Build decision tree for GlaucomaM data set
gm_formula = Class ~ .
gm_ctree = ctree(gm_formula, data = GlaucomaM)
# Plot built tree
plot(gm_ctree)
```
</br>

#### 4.2 Show confusion matrix of the result of the decision tree
```{r}
gm_predict = predict(gm_ctree, GlaucomaM)
table(gm_predict, GlaucomaM$Class)
```
</br>

#### 4.3 Random forest algorithm
```{r}
# Build tree using random forest algorithm
library("randomForest")
gm_formula = Class ~ .
gm_rf = randomForest(gm_formula, data=GlaucomaM, ntree=100, proximity=TRUE)
# Plot error rate as number of trees grows
plot(gm_rf)
```
</br>

#### 4.4 Find out the most important variable for classification
```{r}
importance(gm_rf)
varImpPlot(gm_rf)
```
Looking at the above graph, we can conclude that *vari* is the most important feature for classification.
</br>

## Exercise 5. Support Vector Machine (SVM)

#### 5.1 Build an SVM model for iris data set
```{r}
library("e1071")
iris_formula = Species ~ .
iris_svm = svm(iris_formula, data = iris)
```
</br>

#### 5.2 Plot decision boundary on "Petal.Width" and "Petal.Length"
```{r}
plot(iris_svm, iris, Petal.Width ~ Petal.Length, slice = list(Sepal.Width = 3, Sepal.Length = 4))
```
